Reproduce anaylses of Beninca et al (2008)

### 2016-02-23 code/report.Rmd
report update

T_lags <- 12
num_spp <- length(gams)
rsq_vals <- matrix(NA, T_lags, num_spp)
dimnames(rsq_vals)[[2]] <- names(gams)

for(i in 1:T_lags) {
  gams <- Fit_GAMs(X, gval=1.4, T_lag=i)
  for(j in 1:num_spp)
    rsq_vals[i,j] <- cor(gams[[j]]$fitted.values, gams[[j]]$model[1])^2
}

@@

Quite different patterns from in figure 2 of the nature paper. There is relatively little information in the paper or supplement about how figure 2 data was produced, so difficult to pin down the difference without asking authors.

>>>>

## Some preliminaries, including arranging storage
T_lags <- 12
num_spp <- length(gams)
rsq_vals <- matrix(NA, T_lags, num_spp)
dimnames(rsq_vals)[[2]] <- names(gams)

## fit gams for all the required lags
for(i in 1:T_lags) {
  gams <- Fit_GAMs(X, gval=1.4, T_lag=i)
  ## and get the r-squared for each
  for(j in 1:num_spp)
    rsq_vals[i,j] <- cor(gams[[j]]$fitted.values, gams[[j]]$model[1])^2
}

@@

Some species very similar to figure 2 of the nature paper, some more different. Difference must be due to data in figure 2 coming from neural net models, whereas here it comes from the GAMs. Qualitative result the same as in the original paper, however.
